Depression and suicidality as credible signals of need

### 2021-05-06 Paper.rmd
added parenthetical to show older daughter is the signaler in the thwarted marriage vignette.

**Thwarted marriage vignette**: Indian sample only. Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry. After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive. Any increase in the dowry will come at the younger daughter's expense. The participant therefore proceeds to arrange a marriage to the second man as the first man's family makes arrangements with a different woman.

>>>>

**Thwarted marriage vignette**: Indian sample only. Each participant was asked to imagine that their family was trying to arrange a dowry for their older daughter (the signaler in this vignette) so she can marry a man she already loves, while still saving enough money for their younger daughter's dowry. After the man's family demands more money, the participant's family tries to find a second man, who the older daughter claims to find unattractive. Any increase in the dowry will come at the younger daughter's expense. The participant therefore proceeds to arrange a marriage to the second man as the first man's family makes arrangements with a different woman.
